---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r library and directory, echo = FALSE, message = FALSE}
setwd("C:/Users/Owner/Desktop/ReproResearch/RepData_PeerAssessment1")

library("dplyr")
library(ggplot2)
```

```{r loading and preprocessing, echo = TRUE}
activity = read.csv("activity.csv")

new_activity = na.omit(activity)

new_activity <- new_activity[which(new_activity$steps > 0),]

new_activity <- tbl_df(new_activity)

by_date <- group_by(new_activity, date)
```


## What is mean total number of steps taken per day?

* Calculate the total number of steps taken per day
* Make a histogram of the total number of steps taken each day
* Calculate and report the mean and median of the total number of steps taken per day

```{r Sum of Steps, echo = TRUE, results = 'asis'}
        sum_Results <- summarize(by_date, sum(steps))
        colnames(sum_Results) <- c("Date", "Steps")
        knitr::kable(head(sum_Results))
```


```{r Histogram, echo = TRUE, results = 'asis'}
        hist(sum_Results$Steps, main ="", xlab="Number of Steps taken each Day", ylab = "", breaks = 50)

```


```{r Mean and Median, echo=TRUE}
        mean_Results <- as.integer(mean(sum_Results$Steps))
        median_Results <- median(sum_Results$Steps)
```

The mean is `r mean_Results` and the median is `r median_Results`.

## What is the average daily activity pattern?
* Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
* Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


```{r Daily Activity Pattern}

        by_Interval <- aggregate(steps ~ interval, data = new_activity, FUN =           
                                         mean  )
        plot(by_Interval$interval, by_Interval$steps, type = "l")
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
